---
title: "linregasm"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{linregasm}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Example usage

Here we will demonstrate how to use `linregasm` in a project to check linear regression assumptions:

```{r setup}
library(linregasm)
```

## Define Sample Data
We will use the `Iris` dataset from the `data` package to demonstrate the functionality of `lrasm.`linregasm`.

```{r}
data(iris)
head(iris)

```

In our example, we want to investigate the linear relationship between the response Petal.width versus the predictors: Sepal.Length, Sepal.Width, and petal width. We start by defining the dataframe and a formula to relate the variables within a linear regression model:

```{r}
formula = "Petal.Width ~ Sepal.Length + Sepal.Width + Petal.Length"
iris_df = iris
```

## Test for Homoscedasticity of Residuals

We can evaluate the homoscedasticity of our residuals by passing our dataframe and formula into the function `homoscedasticity`. Note that 'homoscedasticity' returns two objects, the first one is a plot of residuals vs predicted values, while the second is the p value of the correlation between residuals vs predicted values:

```{r}

results <- linregasm::homoscedasticity(iris_df, formula)

results[[1]]
```
